FantasticLamp: a genome graph based pipeline for calculating the efficacy of genomic edits

### 2024-02-01 paper/main.tex
Updated README

% Don't think this applies? Check with Erik
\section*{Data availability}
Code and links to data resources used to build this manuscript and its figures can be found in the paper's public repository: \url{https://github.com/casper-schutte/fantastic-lamp}.

>>>>

% Don't think this applies? Check with Erik
\section*{Data availability}
The scripts that comprise the \textit{FantasticLamp} pipeline, as well as the code and links to data resources used to build this manuscript and its figures, can be found in the paper's public repository: \url{https://github.com/casper-schutte/fantastic-lamp}.
